draft_final_assignment

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
```

@@

@@

ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc > 1.0, "Rep", "NA"))

wide_sentiment_full <- summary_sentiment %>%
  group_by(party, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = party, values_from = score) %>%
  select(-c("Both", "NA")) %>%
  drop_na(Democrat, Republican)

daily_sentiment_115 <- days_115 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```

@@

daily_sentiment_116 <- days_116 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

@@

ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
days_117 <- data.frame(date = seq(as.Date("2021-01-01"),as.Date("2022-12-31"),1))

daily_sentiment_117 <- days_117 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party", values_to="score") %>%
  group_by(party) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
```

@@

ggplot(daily_sentiment, aes(x=date, y = score, colour=party)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
summary_sentiment$party_full <- ifelse(summary_sentiment$cosponsor_D_perc == 1.0, "Dem", ifelse(summary_sentiment$cosponsor_R_perc == 1.0, "Rep", NA))

wide_sentiment_full <- summary_sentiment %>%
  drop_na(party_full) %>%
  group_by(party_full, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = party_full, values_from = score)

daily_sentiment_115 <- days_115 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
  group_by(party_full) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

@@

ggplot(daily_sentiment_115, aes(x=date, y = score, colour=party_full)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```

@@

daily_sentiment_116 <- days_116 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
  group_by(party_full) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

@@

ggplot(daily_sentiment_116, aes(x=date, y = score, colour=party_full)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
```{r}
days_117 <- data.frame(date = seq(as.Date("2021-01-01"),as.Date("2022-12-31"),1))

daily_sentiment_117 <- days_117 %>% 
  left_join(wide_sentiment_full) %>% 
  pivot_longer(cols = -date, names_to="party_full", values_to="score") %>%
  group_by(party_full) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party_full)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
##Some machine learning

```{r}
#Prediction model to see if can predict if bill is Republican or Democrat

#Keep only bills that are over 66% Democrat or Republican
df1 <- df %>%
  filter(party != "Both")

df1 <- df1[sample(nrow(df1)),]
df1$env <- 0
df1$env[df1$party == "Republican"] <- 1
df1$env <- factor(df1$env)

df_split <- initial_split(df1, prop=0.8) 
train_data <- training(df_split) 
test_data <- testing(df_split)

rec <- recipe(env ~ summary, data = train_data) %>% 
  step_tokenize(summary) %>% 
  step_tokenfilter(summary, max_tokens = 1e3) %>% 
  step_tfidf(summary)

model <- svm_linear(mode="classification")

wf <- workflow() %>% 
  add_recipe(rec) %>% 
  add_model(model)

model_fit <- wf %>% 
  fit(train_data)
```

```{r}
test_data$prediction <- predict(model_fit, test_data)$.pred_class

scorer <- metric_set( yardstick::accuracy, 
                      yardstick::precision, 
                      yardstick::recall, 
                      yardstick::f_meas
)

scorer(test_data, truth=env, estimate=prediction, event_level="second")
```

```{r}
#Prediction model to see if can predict if bill is focusing on health (as policy area)

df2 <- df[sample(nrow(df)),]
df2$env <- 0
df2$env[df2$policy_area == "Health"] <- 1
df2$env <- factor(df2$env)

df_split <- initial_split(df2, prop=0.8) 
train_data <- training(df_split) 
test_data <- testing(df_split)

rec <- recipe(env ~ summary, data = train_data) %>% 
  step_tokenize(summary) %>% 
  step_tokenfilter(summary, max_tokens = 1e3) %>% 
  step_tfidf(summary)

model <- svm_linear(mode="classification")

wf <- workflow() %>% 
  add_recipe(rec) %>% 
  add_model(model)

model_fit <- wf %>% 
  fit(train_data)
```

```{r}
test_data$prediction <- predict(model_fit, test_data)$.pred_class

scorer <- metric_set( yardstick::accuracy, 
                      yardstick::precision, 
                      yardstick::recall, 
                      yardstick::f_meas
)

scorer(test_data, truth=env, estimate=prediction, event_level="second")
```
